---
title: "Shiny Diamonds Price Predicter"
author: "Joe Yadush"
date: "November 2, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(UsingR)
data(diamond)
```

## Shiny Diamonds

This is a shiny application designed to predict the expected price of a diamond (in Singapore Dollars) based on the weight of the diamond.


Use the slider to option to look at various weights (measured in carats) of the diamond. A red dot will be plotted
for you showing the predicted value as well as a printout below the plot of the price.

A linear model was fitted to assist in determining the price. You have the option of displaying the fitted line
or not with a checbox option underneath the slider.

## Source code and application locations

- The original code can be found on **GitHub** at <https://github.com/yadushj/shinyDiamonds>.

- The application has been published to  **RPubs** at <https://yadushj.shinyapps.io/diamondprice/>.

## About the data

The data is from the **diamond** dataset requiring the **UsingR** package

The data is a set of 48 diamond rings containing price in Singapore dollars 
based on the size or weight of the diamond (in carats)

```{r diamond, echo = TRUE}
summary(diamond)
```

## Inferring a possible price

A quick plot to give initial indication of price. Dont forget to find
your own price at <https://yadushj.shinyapps.io/diamondprice/>.

```{r}
plot(diamond$carat, diamond$price, xlab = "Carats",
                     ylab = "Price (Sin dollars)", bty = "n", pch = 16,
                     xlim = c(0.15, 0.35), ylim = c(200, 1000))
```

